---
output: pdf_document
classoption: landscape
---
```{r setup, include=FALSE}
# Copyright 2017 The WWU eLectures Team All rights reserved.
#
# Licensed under the Educational Community License, Version 2.0
# (the "License"); you may not use this file except in compliance with
# the License. You may obtain a copy of the License at
#
#     http://opensource.org/licenses/ECL-2.0
#
# Unless required by applicable law or agreed to in writing, software
# distributed under the License is distributed on an "AS IS" BASIS,
# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
# See the License for the specific language governing permissions and
# limitations under the License.

knitr::opts_chunk$set(echo = TRUE)

library('reshape2')
library('dplyr')
library('RJSONIO')
library('ggplot2')
library('knitr')

fromReport <- as.character(input$dateRange[1])
toReport <- as.character(input$dateRange[2])

episodes_count <- subset(episodes_unique, date %in% input$dateRange[1]:input$dateRange[2])
episodes_count <- subset(episodes_count, episodeID %in% input$episodes & seriesID == substr(paste(names(parseQueryString(session$clientData$url_search)), parseQueryString(session$clientData$url_search), sep = "=", collapse=", "), 8, 200))
episodes_count <- aggregate(data = episodes_count, counts ~ Episodes, sum)
colnames(episodes_count) <- c("Episodes", "Hits")

p <- ggplot(subset(episodes_unique, episodeID %in% input$episodes & seriesID == subset(seriesTitles, ID == substr(paste(names(parseQueryString(session$clientData$url_search)), parseQueryString(session$clientData$url_search), sep = "=", collapse=", "), 8, 200))$ID), aes(x = date, y = counts, group = Episodes, color = Episodes)) +
  geom_line() +
  xlab("Date") +
  ylab("Hits") +
  scale_x_date(date_breaks = "1 week") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position="right", legend.title=element_text(size=25) , legend.text=element_text(size=20), legend.key.size=unit(15, "mm")) +
  xlim(input$dateRange) +
  ylim(c(0,max(subset(episodes_unique, seriesID == subset(seriesTitles, ID == substr(paste(names(parseQueryString(session$clientData$url_search)), parseQueryString(session$clientData$url_search), sep = "=", collapse=", "), 8, 200))$ID & date %in% input$dateRange[1]:input$dateRange[2])$counts)))
      
if (input$recDates == TRUE) {
  p <- p + geom_vline(xintercept = as.numeric(as.Date(subset(episodeTitles, ID %in% input$episodes)$Date)), linetype = "longdash")
}
      
```

---
title: "Zugriffe auf `r names(subset(series, series %in% substr(paste(names(parseQueryString(session$clientData$url_search)), parseQueryString(session$clientData$url_search), sep = "=", collapse=", "), 8, 200)))`"
author: "eLectures Supportstelle"
---
Generiert am: `r Sys.Date()`

**Zeitraum**

Start: `r as.Date(fromReport)`

Ende: `r as.Date(toReport)`

## Zugriffe pro Aufnahme
In dem Zeitraum von `r as.Date(fromReport)` bis `r as.Date(toReport)` wurde `r sum(episodes_count$Hits)` Mal auf Ihre Aufnahmen zugegriffen. Die folgende Tabelle zeigt Ihnen die Zugriffe pro Aufnahme in diesem Zeitraum.

```{r episodestable, echo=FALSE}
kable(episodes_count)
```

Der folgende Plot zeigt die Verteilung dieser Zugriffe über den gegebenen Zeitraum per Aufnahme. Die gestrichelten Linien zeigen einen Aufnahmetag.

```{r episodesfigure, echo=FALSE, fig.height=15, fig.width=20, warning=FALSE}
print(p)
```
